HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-09-11 paper/main.tex
for camera ready

\documentclass[11pt,letterpaper]{article}
%\usepackage[round]{natbib}
\usepackage{emnlp2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
\usepackage{titlesec}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\usepackage[font={small}]{caption}

\def\emnlppaperid{***}
\setlength{\belowcaptionskip}{-10pt}

@@

\titlespacing{\section}{2pt}{*0}{*0}
\titlespacing{\subsection}{2pt}{*0}{*0}
\titlespacing{\subsubsection}{2pt}{*0}{*0}
\titlespacing{\paragraph}{1pt}{*0}{3pt}

@@

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{\S\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\XXX}[1]{}
%\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
\newcommand{\oa}[1]{}
\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
%\newcommand{\bh}[1]{}

@@

@@

\author{Author 1\\
	    XYZ Company\\
	    111 Anywhere Street\\
	    Mytown, NY 10000, USA\\
	    {\tt author1@xyz.org}
	  \And
	Author 2\\
  	ABC University\\
  	900 Main Street\\
  	Ourcity, PQ, Canada A1A 1T2\\
  {\tt author2@abc.ca}}

@@

Human evaluation of machine translation normally uses sentence-level measures such as relative ranking or adequacy scales. However these provide no insight into possible errors,
and do not scale well with sentence length.
We argue for a semantics-based evaluation, which captures what meaning components
are retained in the MT output, providing a more fine-grained analysis of
translation quality, and enables the construction and tuning of semantics-based MT. 
We present a novel human semantic evaluation measure, Human
UCCA-based MT Evaluation (HUME), building on the UCCA semantic representation scheme.
%Making progress over previous work, the proposed measure takes into account
HUME covers
a wider range of semantic phenomena than previous methods and does not rely on semantic annotation
of the potentially garbled MT output. 
%itself, whose interpretation is often unclear.
We experiment with four language pairs, demonstrating HUME's broad applicability,
and report good
%as well as its reliability, reflected in its 
inter-annotator agreement rates and 
 correlation with human adequacy scores.

@@

These problems are partially addressed by measures that decompose over parts of the evaluated
translation. For automatic measures,
these are often words or n-grams, for manual measures some structural
information is taken into account \parcite{machacek:bojar:segranks:2015}, or the
annotators are explicitly asked to mark errors, which however suffers from even
lower agreement than ranking \parcite{lommel:etal:mqm-iaa:2014}.
% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
A promising line of research decomposes metrics
over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is HMEANT
\parcite{lo2011structured}.
%More recent work on MT evaluation proposed measures
%that decompose

@@

HUME operates by aggregating human assessments of the translation quality of individual
semantic units in the source sentence. We 
%HUME only requires semantically annotating the source sentence,
are thus avoiding the semantic annotation of machine-generated text,
which is often garbled or semantically unclear.
This also allows the re-use of the source semantic annotation for
measuring the quality of different translations of the same source sentence,
and 
%By basing the measure on a direct comparison
%of the source and translation we avoid the difficulties created by using
avoids relying on possibly suboptimal reference translations.
%albeit at the cost of requiring the
%evaluator to be proficient in both the source and target languages.
%An elaborate comparison of HUME and HMEANT is given in \secref{sec:hmeant_comp}.

@@

%These difficulties have motivated the definition of a human measure that decomposes over
%the semantic structure of the sentence, rather than its n-grams. The most notable attempt of
%this type is the MEANT measure, and its human variant HMEANT
%\parcite{lo2010evaluating,lo2011structured,Lo2011meant,lo2013meant}, which quantifies the
%similarity between the output translation and a reference translation in terms of the similarity
%between their verbal argument structures
%While the measure addresses the two major shortcomings
%detailed above, it is unable to capture semantic differences which do not show up in
%the verb-argument structure, including several very frequent phenomena, such as
%inter-clause linkage, nominalizations and copula clauses
%(see \secref{sec:hmeant_comp}).
%Another shortcoming of MEANT is its reliance on semantically annotating MT output,
%which is often unintelligible. Finally, measures based on a comparison to a
%reference translation
%are necessarily incomplete, as they compare to a small number of references
%out of the the huge number of possible translations a sentence may have
%\parcite{dreyer2012hyter}.

\paragraph{MT Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language
%\parcite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT tasks \parcite{bojar2015findings}, or by assigning
adequacy/fluency scores to each translation, a procedure recently improved
by \perscite{graham2015accurate}.
However, while providing the gold standard for MT evaluation, human evaluation
is not a scalable solution.
%and is infeasible where a wide variety of systems or parameter settings are to be evaluated.
% has motivated the construction of cheaper methods that correlate with human
%judgement.

Scalability is addressed by employing automatic and semi-automatic approximations of human
judgements. Commonly, such scores decompose over the sub-parts of
the translation, and quantify how many of these sub-parts appear in a manually created reference translation.
This decomposition allows system developers
to localize the errors.
%, or at least unconfirmed parts within the translation.
The most commonly used measures decompose over n-grams or individual words, e.g., 
BLEU \parcite{Papineni:2002}, NIST \parcite{Doddington:2002} and METEOR
\parcite{Banerjee:2005}.
Another common approach is to determine the similarity between the reference and translation
in terms of string edits \parcite{snover2006study}.
While these measures stimulated much progress in MT research by allowing
the evaluation of massive-scale experiments, the focus on words and n-grams does
not provide a good estimate of semantic correctness, and may favour shallow string-based
MT models.

@@

In order to address this shortcoming, more recent work quantified
the similarity of the reference and translation in terms
of their structure. \perscite{liu2005syntactic} took a syntactic approach, 
using dependency grammar, and
\perscite{owczarzak2007evaluating} took a similar approach using lexical-functional grammar structures.
\perscite{gimenez2007linguistic} proposed to combine multiple types of information,
capturing the overlap between the translation and reference in terms of their
semantic (predicate-argument structures), lexical and morphosyntactic features.

@@

\paragraph{Semantic Representation.}
UCCA (Universal Conceptual Cognitive Annotation, \inparcite{abend2013universal}) is a
cross-linguistically applicable, lightweight
scheme for semantic annotation. Formally, an UCCA structure is a directed acyclic graph (DAG),
whose leaves correspond to the words of the text.
The graph's nodes, called {\sc units}, are either terminals or several elements jointly
viewed as a single entity according to some semantic or cognitive consideration. Edges bear
a category, indicating the role of the sub-unit in the structure the unit
represents.

UCCA's current inventory of distinctions focuses on argument structures
(adjectival, nominal, verbal and others) and relations between them.
The most basic notion is the Scene, which describes a movement, an
action or a state which persists in time. Each Scene contains one main
relation and zero or more participants. For example, the sentence ``After graduation, Tom moved to NYC''
contains two Scenes, whose main relations are ``graduation'' and ``moved''.
The participant ``Tom'' is a part of both Scenes, while ``NYC'' only of the
latter (\figref{fig:ucca_example_v2}). Further categories account for
inter-scene relations and the sub-structures of participants and relations.

% UCCA Motivation
The use of UCCA for semantic MT evaluation measure is motivated by two main reasons. 
First, UCCA's set of categories can
be reliably annotated by non-experts after as little as two hours
of training \parcite{marinotti2014}.
Second, UCCA is cross-linguistically applicable, seeking to
represent what is shared between languages by building on
linguistic typological theory \parcite{Dixon:10a,Dixon:10b,Dixon:12}.
Its cross-linguistic applicability has so far been tested in annotations of
English, French, German and Czech.
%Third, the scheme has been shown to be stable across translations:
%UCCA annotations of translated text usually contain the same set of relations
%\parcite{sulem2015conceptual}, indicating that the scheme reflects
%a common layer of representation that in a correct translation
%is mostly shared between the translation and the source.

@@

The Abstract Meaning Representation (AMR) \parcite{banarescu2013abstract} project
shares UCCA's motivation for defining a more complete semantic annotation.
However, using AMR is not optimal for defining a decomposition of a sentence into semantic
units as it does not ground its semantic symbols in the text,
and thus does not provide clear decomposition of the sentence into sub-units.
Also, AMR is more fine-grained than UCCA and consequently harder to annotate.
Other approaches represent semantic structures as bi-lexical dependencies
\parcite{sgallhp:1986,hajic2012announcing,oepen2006discriminant},
which are indeed grounded in the text, but are less suitable for MT evaluation
as they require linguistic expertise for their annotation.

@@

\vspace{-.1em}
\section{The HUME Measure}\label{sec:hume}
\vspace{-.2em}

@@

This section summarises the manual annotation procedure used
to compute the HUME measure. 
We denote the source sentence as $s$ and the translation as $t$. 
The procedure involves two manual steps: (1) UCCA-annotating $s$, 
(2) human judgements as to the translation quality of each semantic unit of $s$ relative to $t$,
where units are defined according to the UCCA annotation.
UCCA annotation is performed once for every source sentence,
irrespective of the number of its translations we wish
to evaluate
%\footnote{Instead of relying on the source,
%the evaluation could be based on the UCCA structure for the \emph{reference}
%translation.
%More details in the discussion in \secref{src-vs-ref}.
% This would allow monolingual annotators to take part in the
% evaluation. On the downside, the translation would have to be aligned to the
% reference and more importantly, we would risk inaccurate judgements due to
% the naturally occurring differences between the source and its reference
% translations.
%}.

@@

Annotation of the semantic units requires first deciding whether
a unit is {\it structural}, i.e., has meaning-bearing sub-units also in the
target language,
or {\it atomic}. In most cases, atomic units
correspond to individual words, but they may also correspond to unanalyzable
multi-word expressions.
When a multi-word unit is labeled as atomic, its sub-units' annotations are ignored
in the evaluation.

Atomic units can be labelled as ``Green'' (correct), ``Orange'' (partially correct)
and ``Red'' (incorrect). 
Green means that the meaning of the word or phrase has been largely preserved.
Orange means that the essential meaning of the unit has been preserved,
but some part of the translation is wrong.
This is often be due to the translated word having the the wrong inflection,
in a way that impacts little on the understandability of the sentence.
Red means that the essential meaning of the unit has not been captured.

Structural units have sub-units (children in the UCCA graph),
which are themselves atomic or structural.
% Ondrej thinks the following can be simply removed:
%The labels assigned to such nodes reflect the extent to which
%the relation between the sub-units is preserved in $t$.
%\XXX{(BH: don't follow this) For instance, a Scene unit represents the relation between the
%Scene elements, such as the predicate (main relation), participants and adverbials.}
Structural units are labeled as ``Adequate'' or ``Bad'', meaning
that the relation between the sub-units went wrong\footnote{
  Three labels are used with atomic units, as opposed to two labels with structural units,
as atomic units are more susceptible to slight errors.}.
%here are three major cases where the relationship between the children might go
%wrong in translation and 
We will use the example ``man bites dog'' to illustrate typical examples of why a structural node
should be labelled as ``Bad'':
incorrect ordering (``dog bites man''), 
deletion (``man bites'') and insertion (``man bites biscuit dog''). 
%First, the components of the translation may be ordered differently from the source,
%such that the relation between them changes. For instance, if
%the sentence ``man bites dog'' is translated into a sentence meaning ``dog bites man'',
%the semantic unit corresponding to the Scene will be marked as Bad, while
%the individual atomic units ``dog'', ``bites'' and ``man'' will be marked as Green.
%Second, A superfluous word or phrase may be inserted into
%the translation. For instance, if ``dog bites man'' is translated into ``dog viciously bites man''.
%Third, one of the sub-units may be missing from the translation.
%For instance, if ``dog bites man'' is translated into ``dog bites''.

@@

\vspace{-.5cm}
{\scriptsize
\begin{equation}
  \HUME(s,t) = \frac{\Green(s,t) + \Adequate(s,t) + 0.5\cdot \Orange(s,t)}{\Units(s)}
  \nonumber
\end{equation}
}
\vspace{-.5cm}

@@

\figref{fig:interface} shows the HUME annotation interface.
% We now describe the HUME annotation interface, shown in \figref{fig:interface}. 
% %We turn to discuss the interface for collecting human judgements on the semantic units
% %of the source, relating to the translation. 
% UCCA annotations of the source are done offline,
% using the UCCA web application.
% %\figref{fig:interface} presents the user interface of HUME. 
% The translation appears at the top, and
% the source sentence directly below it. Underneath the source sentence appears
% its list of semantic units. 
% %For each semantic unit, including the one for the
% %entire source sentence, there is a textbox, displaying the yield of that unit.
% %Information on the category of the unit (e.g., whether it is a Scene, participant etc.).
The user is asked to select a label for each source semantic unit,
by clicking the ``A'', ``B'', Green, Orange, or Red buttons to the right of the unit's box.
Units with multiple parents (as with ``Tom'' in \figref{fig:hume_tree_v2}) are displayed
twice, once under each of their parents, but are only annotatable in one of
their instances, to avoid double counting.
%Note that the UCCA labels are not shown.

@@

For example, 
%consider the sentence $s=$``We're driving back on Friday'' and the German
%translation t=``Am Freitag fahren wir zur\"uck'' (lit. ``on Friday driving we back'').
%``driving back'' will be aligned to ``fahren ... zur\"uck'',
%and ``wir'' will be marked as intervening word. Another example
in \figref{fig:interface}, ``ongoing pregnancy'' is translated to
``Schwangerschaft ... laufenden'' (lit. ``pregnancy ... ongoing''). This alone
seems acceptable but the interleaving words in red notify the annotator to check
the whole translation, in which the meaning of the expression is not preserved.
The annotator should thus mark this structural node as Bad.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \parcite{Koehn:2007}.  These were trained on large parallel data sets extracted from
OPUS \parcite{tiedemann:2009}, and the data sets released for the WMT14
medical translation task \parcite{bojar-EtAl:2014:W14-33}, 
giving between 45 and 85 million sentences of training data, depending on language pair.
%\oa{I think we should probably
%  say how many in each.}.
% ... if someone asks us to do so...
These translation systems were used to translate texts derived from both NHS
24\footnote{\url{http://www.nhs24.com/}} and
Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages.
NHS~24 is a public body providing healthcare and health-service
related information in Scotland, Cochrane is an international NGO
which provides independent systematic reviews on health-related research.
NHS~24 texts come from the ``Health A-Z'' section in the NHS Inform
website, and Cochrane texts come from their plain language summaries
and abstracts.

@@

\begin{figure}[t]
\includegraphics[width=0.45\textwidth]{humevsDAcorrtypes-10en-dero.pdf}
\caption{Pearson correlation of HUME vs. DA scores for en-ro and en-de.
%different node types for both
%  the en-de and en-ro experiments.
Each bar represents a correlation between DA and an aggregate HUME score
based on a sub-set of the units (\#nodes for the en-de/en-ro setting in brackets):
all units ('all', 8624/10885), atomic ('atomic', 5417/6888) and structural units ('struct', 3207/3997),
and units by UCCA categories: Scene main relations (i.e, Process and State units; 'P and S', 954/1178), Parallel Scenes ('H', 656/784),
Participants ('A', 1348/1746),
Centres ('C', 1904/2474), elaborators ('E', 1608/2031) and linkers ('L', 261/315).
%  See text for the bar legend.
%Struct refers to all structural nodes, P+S are all process and state nodes, H parallel scene nodes, A participant, C centre, E elaborators, and L linker nodes.}
\label{fig:dacorrelationtypes}}
\end{figure}

@@

We discuss the main differences between HUME and HMEANT,
a human MT evaluation metric that measures the overlap between the translation a reference
in terms of their SRL annotations.

@@

\vspace{-.3em}
\begin{center}
\begin{tabular}{lp{5.4cm}}
Source & \small a coronary angioplasty may not be technically possible \\
Transl.& \small eine koronare Angioplastie kann nicht technisch m{\"o}glich \\
Gloss & \small a coronary angioplasty can not technically possible \\
\end{tabular}
\end{center}
\vspace{-.5em}

@@

The German translation 
is largely correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign the
sentence a very low score, as it failed to translate the main verb.
%
Conversely, HMEANT does not penalize errors such as tense or negation
flip in a correctly aligned predicate.

%This focus on verbal predicates has a number of unfortunate consequences. We show an example below:

% \noindent
% \begin{inparadesc}
% \item[Source ] a coronary angioplasty may not be technically possible \\
% \item[Transl.] eine koronare Angioplastie kann nicht technisch m{\"o}glich \\
% \item[Gloss ]  a coronary angioplasty can not technically possible \\
% \end{inparadesc}

\com{
}

>>>>

\documentclass[11pt,letterpaper]{article}
%\usepackage[round]{natbib}
\usepackage{acl2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{pgfplotstable}
\usepackage{titlesec}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\usepackage[font={small}]{caption}
%\usepackage{hyperref}

\aclfinalcopy

\def\emnlppaperid{***}
%\setlength{\belowcaptionskip}{-10pt}

@@

%\titlespacing{\section}{2pt}{*0}{*0}
%\titlespacing{\subsection}{2pt}{*0}{*0}
%\titlespacing{\subsubsection}{2pt}{*0}{*0}
%\titlespacing{\paragraph}{1pt}{*0}{3pt}

@@

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{\S\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\XXX}[1]{}
\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
\newcommand{\oamod}[1]{{\color{red}#1}}

%\newcommand{\oa}[1]{}
\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
%\newcommand{\bh}[1]{}

@@

\newcommand{\GrantNo}{644402}
\newcommand{\ProjectName}{HimL}
\newcommand{\ProjectType}{Horizon 2020 Innovation Action}

@@

\author{
  Alexandra Birch\textsuperscript{1}, Omri Abend\textsuperscript{2}, Ond{\v{r}}ej Bojar\textsuperscript{3},
  Barry Haddow\textsuperscript{1}\\
\textsuperscript{1}School of Informatics, University of Edinburgh\\
\textsuperscript{2}School of Computer Science and Engineering, Hebrew University of Jerusalem\\
\textsuperscript{3} Charles University in Prague, Faculty of Mathematics and Physics\\
\texttt{a.birch@ed.ac.uk, oabend@cs.huji.ac.il}\\
\texttt{bojar@ufal.mff.cuni.cz, bhaddow@inf.ed.ac.uk}\\
}

@@

Human evaluation of machine translation normally uses sentence-level measures such as relative ranking or adequacy scales. However, these provide no insight into possible errors,
and do not scale well with sentence length.
We argue for a semantics-based evaluation, which captures what meaning components
are retained in the MT output, thus providing a more fine-grained analysis of
translation quality, and enabling the construction and tuning of semantics-based MT. 
We present a novel human semantic evaluation measure, Human
UCCA-based MT Evaluation (HUME), building on the UCCA semantic representation scheme.
%Making progress over previous work, the proposed measure takes into account
HUME covers
a wider range of semantic phenomena than previous methods and does not rely on semantic annotation
of the potentially garbled MT output. 
%itself, whose interpretation is often unclear.
We experiment with four language pairs, demonstrating HUME's broad applicability,
and report good
%as well as its reliability, reflected in its 
inter-annotator agreement rates and 
 correlation with human adequacy scores.

@@

These problems are partially addressed by measures that decompose over parts of the evaluated
translation, often words or n-grams (see \secref{sec:background} for a brief survey of previous
work). A promising line of research decomposes metrics
over semantically defined units, quantifying the similarity of the output and the
reference in terms of their verb argument structure; the most notable of these measures is HMEANT
\parcite{lo2011structured}.

% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
%More recent work on MT evaluation proposed measures
%that decompose

@@

HUME operates by aggregating human assessments of the translation quality of individual
semantic units in the source sentence. We 
are thus avoiding the semantic annotation of machine-generated text,
which is often garbled or semantically unclear.
This also allows the re-use of the source semantic annotation for
measuring the quality of different translations of the same source sentence,
and avoids relying on possibly suboptimal reference translations.

%By basing the measure on a direct comparison
%of the source and translation we avoid the difficulties created by using
%albeit at the cost of requiring the
%evaluator to be proficient in both the source and target languages.
%An elaborate comparison of HUME and HMEANT is given in \secref{sec:hmeant_comp}.

@@

%These difficulties have motivated the definition of a human measure that decomposes over
%the semantic structure of the sentence, rather than its n-grams. The most notable attempt of
%this type is the MEANT measure, and its human variant HMEANT
%\parcite{lo2010evaluating,lo2011structured,Lo2011meant,lo2013meant}, which quantifies the
%similarity between the output translation and a reference translation in terms of the similarity
%between their verbal argument structures
%While the measure addresses the two major shortcomings
%detailed above, it is unable to capture semantic differences which do not show up in
%the verb-argument structure, including several very frequent phenomena, such as
%inter-clause linkage, nominalizations and copula clauses
%(see \secref{sec:hmeant_comp}).
%Another shortcoming of MEANT is its reliance on semantically annotating MT output,
%which is often unintelligible. Finally, measures based on a comparison to a
%reference translation
%are necessarily incomplete, as they compare to a small number of references
%out of the huge number of possible translations a sentence may have
%\parcite{dreyer2012hyter}.

\paragraph{MT Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language
%\parcite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT tasks \parcite{bojar2015findings}, or by assigning
adequacy/fluency scores to each translation, a procedure recently improved
by \perscite{graham2015accurate}.
Some manual measures ask annotators to explicitly mark errors, which however
suffers from even lower agreement than ranking \parcite{lommel:etal:mqm-iaa:2014}.

However, while providing the gold standard for MT evaluation, human evaluation
is not a scalable solution.
Scalability is addressed by employing automatic and semi-automatic approximations of human
judgements. Commonly, such scores decompose over the sub-parts of
the translation, and quantify how many of these sub-parts appear in a manually
created reference translation.
This decomposition allows system developers to localize the errors.
The most commonly used measures decompose over n-grams or individual words, e.g., 
BLEU \parcite{Papineni:2002}, NIST \parcite{Doddington:2002} and METEOR \parcite{Banerjee:2005}.
Another common approach is to determine the similarity between the reference and translation
in terms of string edits \parcite{snover2006study}.
While these measures stimulated much progress in MT research by allowing
the evaluation of massive-scale experiments, the focus on words and n-grams does
not provide a good estimate of semantic correctness, and may favour shallow string-based
MT models.

%and is infeasible where a wide variety of systems or parameter settings are to be evaluated.
% has motivated the construction of cheaper methods that correlate with human
%judgement.

@@

In order to address this shortcoming, more recent work quantified
the similarity of the reference and translation in terms
of their structure. \perscite{liu2005syntactic} took a syntactic approach, 
using dependency grammar, and
\perscite{owczarzak2007evaluating} took a similar approach using lexical-functional grammar structures.
\perscite{gimenez2007linguistic} proposed to combine multiple types of information,
capturing the overlap between the translation and reference in terms of their
semantic (predicate-argument structures), lexical and morphosyntactic features.
\perscite{machacek:bojar:segranks:2015} divided the source sentences into shorter segments,
defined using a phrase structure parse, and applied human ranking to the resulting segments.\oa{is this description OK?}

@@

\paragraph{Semantic Representation.}
UCCA (Universal Conceptual Cognitive Annotation, \inparcite{abend2013universal}) is a
cross-linguistically applicable scheme for semantic annotation.
Formally, an UCCA structure is a directed acyclic graph (DAG),
whose leaves correspond to the words of the text.
The graph's nodes, called {\sc units}, are either terminals or several elements jointly
viewed as a single entity according to some semantic or cognitive consideration. Edges bear
a category, indicating the role of the sub-unit in the structure the unit
represents.

UCCA's basic inventory of distinctions (its {\it foundational layer})
focuses on argument structures (adjectival, nominal, verbal and others)
and relations between them. The most basic notion is the Scene, which describes a movement, an
action or a state which persists in time. Each Scene contains one main
relation and zero or more participants. For example, the sentence ``After graduation, Tom moved to NYC''
contains two Scenes, whose main relations are ``graduation'' and ``moved''.
The participant ``Tom'' is a part of both Scenes, while ``NYC'' only of the
latter (\figref{fig:ucca_example_v2}). Further categories account for
inter-scene relations and the sub-structures of participants and relations.

% UCCA Motivation
The use of UCCA for semantic MT evaluation measure is motivated by two main reasons. 
First, UCCA's foundational layer can
be reliably annotated by non-experts after as little as two hours
of training \parcite{marinotti2014}.
Second, UCCA is cross-linguistically applicable, seeking to
represent what is shared between languages by building on
linguistic typological theory \parcite{Dixon:10a,Dixon:10b,Dixon:12}.
Its cross-linguistic applicability has so far been tested in annotations of
English, French, German and Czech.
Third, the scheme has been shown to be stable across translations:
UCCA annotations of translated text usually contain the same set of relations
\parcite{sulem2015conceptual}, indicating that UCCA reflects a layer of
representation that in a correct translation is mostly shared between
the translation and the source.

@@

The Abstract Meaning Representation (AMR) \parcite{banarescu2013abstract} project
shares UCCA's motivation for defining a more complete semantic annotation.
However, using AMR is not optimal for defining a decomposition of a sentence into semantic
units as it does not anchor its semantic symbols in the text,
and thus does not provide clear decomposition of the sentence into sub-units.
Also, AMR is more fine-grained than UCCA and consequently harder to annotate.
Other approaches represent semantic structures as bi-lexical dependencies
\parcite{sgallhp:1986,hajic2012announcing,oepen2006discriminant},
which are indeed anchored in the text, but are less suitable for MT evaluation
as they require linguistic expertise for their annotation.

@@

\section{The HUME Measure}\label{sec:hume}

@@

This section summarises the manual annotation procedure used
to compute the HUME measure. 
We denote the source sentence as $s$ and the translation as $t$. 
The procedure involves two manual steps: (1) UCCA-annotating $s$, 
(2) HUME-annotation: human judgements as to the translation quality of each semantic
unit of $s$ relative to $t$,
where units are defined according to the UCCA annotation.
UCCA annotation is performed once for every source sentence,
irrespective of the number of its translations we wish to evaluate,
and requires proficiency in the source language only.
HUME annotation requires the employment of bilingual annotators
\footnote{Where bilingual annotators are not available,
  the evaluation could be based on the UCCA structure for the
  \emph{reference} translation. See discussion in \secref{sec:hmeant_comp}.}

@@

Annotation of the semantic units requires first deciding whether
a unit is {\it structural}, i.e., has meaning-bearing sub-units also in the
target language, or {\it atomic}.
In most cases, atomic units
correspond to individual words, but they may also correspond to
multi-word expressions that translate as one unit. \oamod{For instance,
the expression ``took a shower'' is translated into the German ``duschte'',
while its individual words do not correspond to any sub-part of the German translation,
motivating the labeling the entire expression as an atomic node.}
When a multi-word unit is labeled as atomic, its sub-units' annotations are ignored
in the evaluation.

Atomic units can be labelled as ``Green'' (G, correct), ``Orange'' (O, partially correct)
and ``Red'' (R, incorrect). 
Green means that the meaning of the word or phrase has been largely preserved.
Orange means that the essential meaning of the unit has been preserved,
but some part of the translation is wrong.
This is often be due to the translated word having the wrong inflection,
in a way that impacts little on the understandability of the sentence.
Red means that the essential meaning of the unit has not been captured.

Structural units have sub-units (children in the UCCA graph),
which are themselves atomic or structural.
% Ondrej thinks the following can be simply removed:
%The labels assigned to such nodes reflect the extent to which
%the relation between the sub-units is preserved in $t$.
%\XXX{(BH: don't follow this) For instance, a Scene unit represents the relation between the
%Scene elements, such as the predicate (main relation), participants and adverbials.}
Structural units are labeled as ``Adequate'' (A) or ``Bad'' (B), meaning
that the relation between the sub-units went wrong\footnote{
  Three labels are used with atomic units, as opposed to two labels with structural units,
as atomic units are more susceptible to slight errors.}.
%here are three major cases where the relationship between the children might go
%wrong in translation and 
We will use the example ``man bites dog'' to illustrate typical examples of why a structural node
should be labelled as ``Bad'':
incorrect ordering (``dog bites man''), 
deletion (``man bites'') and insertion (``man bites biscuit dog''). 
%First, the components of the translation may be ordered differently from the source,
%such that the relation between them changes. For instance, if
%the sentence ``man bites dog'' is translated into a sentence meaning ``dog bites man'',
%the semantic unit corresponding to the Scene will be marked as Bad, while
%the individual atomic units ``dog'', ``bites'' and ``man'' will be marked as Green.
%Second, A superfluous word or phrase may be inserted into
%the translation. For instance, if ``dog bites man'' is translated into ``dog viciously bites man''.
%Third, one of the sub-units may be missing from the translation.
%For instance, if ``dog bites man'' is translated into ``dog bites''.

@@

\vspace{-.3cm}

{\scriptsize
\begin{equation}
  \HUME(s,t) = \frac{\Green(s,t) + \Adequate(s,t) + 0.5\cdot \Orange(s,t)}{\Units(s)}
  \nonumber
\end{equation}
}

\vspace{-.5cm}

@@

\figref{fig:interface} shows the HUME annotation interface\footnote{A demo of HUME
  can be found in \url{www.cs.huji.ac.il/~oabend/hume_demo.html}}.
% We now describe the HUME annotation interface, shown in \figref{fig:interface}. 
% %We turn to discuss the interface for collecting human judgements on the semantic units
% %of the source, relating to the translation. 
% UCCA annotations of the source are done offline,
% using the UCCA web application.
% %\figref{fig:interface} presents the user interface of HUME. 
% The translation appears at the top, and
% the source sentence directly below it. Underneath the source sentence appears
% its list of semantic units. 
% %For each semantic unit, including the one for the
% %entire source sentence, there is a textbox, displaying the yield of that unit.
% %Information on the category of the unit (e.g., whether it is a Scene, participant etc.).
\oamod{One source sentence and one translation are presented at a time.}
The user is asked to select a label for each source semantic unit,
by clicking the ``A'', ``B'', Green, Orange, or Red buttons to the right of the unit's box.
Units with multiple parents (as with ``Tom'' in \figref{fig:hume_tree_v2}) are displayed
twice, once under each of their parents, but are only annotatable in one of
their instances, to avoid double counting.

@@

For example, 
%consider the sentence $s=$``We're driving back on Friday'' and the German
%translation t=``Am Freitag fahren wir zur\"uck'' (lit. ``on Friday driving we back'').
%``driving back'' will be aligned to ``fahren ... zur\"uck'',
%and ``wir'' will be marked as intervening word. Another example
in \figref{fig:interface}, ``ongoing pregnancy'' is translated to
``Schwangerschaft ... laufenden'' (lit. ``pregnancy ... ongoing''). This alone
seems acceptable but the interleaving words in red notify the annotator to check
the whole translation, in which the meaning of the expression is not
preserved\footnote{The interleaving words are ``... und beide berichtet berichteten ...'' (lit.
  ``... and both report reported ...''), which doesn't form any coherent relation with the rest
  of the sentence.}.
The annotator should thus mark this structural node as Bad.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \parcite{Koehn:2007}.  These were trained on large parallel data sets extracted from
OPUS \parcite{tiedemann:2009}, and the data sets released for the WMT14
medical translation task \parcite{bojar-EtAl:2014:W14-33}, 
giving between 45 and 85 million sentences of training data, depending on language pair.
%\oa{I think we should probably
%  say how many in each.}.
% ... if someone asks us to do so...
These translation systems were used to translate texts derived from both NHS
24\footnote{\url{http://www.nhs24.com/}} and
Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages.
NHS~24 is a public body providing healthcare and health-service
related information in Scotland; Cochrane is an international NGO
which provides independent systematic reviews on health-related research.
NHS~24 texts come from the ``Health A-Z'' section in the NHS Inform
website, and Cochrane texts come from their plain language summaries
and abstracts.

@@

\begin{figure}[t]
\includegraphics[width=0.45\textwidth]{humevsDAcorrtypes-10en-dero.pdf}
\caption{Pearson correlation of HUME vs. DA scores for en-ro and en-de.
%different node types for both
%  the en-de and en-ro experiments.
Each bar represents a correlation between DA and an aggregate HUME score
based on a sub-set of the units (\#nodes for the en-de/en-ro setting in brackets):
all units (``all'', 8624/10885), atomic (``atomic'', 5417/6888)
and structural units (``struct'', 3207/3997),
and units by UCCA categories: Scene main relations
(i.e, Process and State units; ``P and S'', 954/1178), Parallel Scenes (``H'', 656/784),
Participants (``A'', 1348/1746),
Centres (``C'', 1904/2474), elaborators (``E'', 1608/2031) and linkers (``L'', 261/315).
%  See text for the bar legend.
%Struct refers to all structural nodes, P+S are all process and state nodes, H parallel scene nodes, A participant, C centre, E elaborators, and L linker nodes.}
\label{fig:dacorrelationtypes}}
\end{figure}

@@

\oa{This entire section needs reviewing}

We discuss the main differences between HUME and HMEANT,
a human MT evaluation metric that measures the overlap between the translation a reference
in terms of their SRL annotations. The discussion is acoompanied by examples from our
experimental data.

@@

\begin{center}
\begin{tabular}{lp{5.4cm}}
Source & \small a coronary angioplasty may not be technically possible \\
Transl.& \small eine koronare Angioplastie kann nicht technisch m{\"o}glich \\
Gloss & \small a coronary angioplasty can not technically possible \\
\end{tabular}
\end{center}

@@

The German translation is largely correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign the
sentence a very low score, as it failed to translate the main verb.

Conversely, HMEANT does not penalize errors (e.g., partial semantic compatability,
or negation flip) in a correctly aligned predicate:

\begin{center}
\begin{tabular}{lp{5.4cm}}
Source & \small ... don't skip meals ... \\
Transl.& \small ... nicht {\"u}berspringen Mahlzeiten ... \\
Gloss & \small don't skip meals ... \\
\end{tabular}
\end{center}
